\LARGE How coexistence mechanisms mediate temporal stability

### 2014-11-19 manuscript/ms_CoexistStability.Rnw
udpated fig in ms

\subsection{Implementing relative nonlinearity}
When considering consumer-resource dynamics, species coexistence by relative nonlinearity requires that each species has different nonlinear responses to resource availability, and resource availability must fluctuate through time. In a constant resource environment, the species with the lowest R* will always exclude the other species.

\begin{figure}
\begin{center}
<<echo=FALSE, fig=TRUE,jpeg=TRUE,height=3, width=8.5 >>=
source("../modelCode/continuousRelativeNonlinearity_CR.R")
@
\end{center}
\caption{Example time-series from our pulsed consumer-resource model where $g_{1,2}=1$, but species have different nonlinear uptake rate responses to resource supply (A). Species 2 has the lowest R* but its resource response saturates at a lower level than species 2. Species 1 is orange, species 2 is purple. The far right panel shows the population, by species, and community-level coefficient of variation.}
\end{figure}

>>>>

\subsection{Implementing relative nonlinearity}
When considering consumer-resource dynamics, species coexistence by relative nonlinearity requires that each species has different nonlinear responses to resource availability, and resource availability must fluctuate through time. In a constant resource environment, the species with the lowest R* will always exclude the other species. So we can compare this model to the storage effect model, we still allow the germination rate \emph{g} to vary, but both species are perfectly correlate -- that is, $\rho=1$.

\begin{figure}
\begin{center}
<<echo=FALSE, fig=TRUE,jpeg=TRUE,height=3, width=8.5 >>=
source("../modelCode/continuousRelativeNonlinearity_CR_v2.R")
@
\end{center}
\caption{Example time-series from our pulsed consumer-resource model where $g_{1,2}=1$, but species have different nonlinear uptake rate responses to resource supply (A). Species 2 has the lowest R* but its resource response saturates at a lower level than species 2. Species 1 is orange, species 2 is purple. The far right panel shows the population, by species, and community-level coefficient of variation.}
\end{figure}
